Mahotas: Open source software for scriptable computer vision

### 2013-04-23 paper.tex
REF New reference to work using mahotas

\textbf{Dependencies}\\
It requires numpy to be present and installed.

@@

Originally, this code was developed in the context of cellular image analysis.
However, none of the functionality is specific to this context and many
computer vision pipelines can make use of it.

This package (and earlier versions of it) have been used by
myself~\citep{Coelho2009,Coelho2010a} and close collaborators in several
publications~\citep{omerosearcher}. Other groups have used in published work,
both in cell image analysis~\citep{CYTO:CYTO22034} and in other
areas~\citep{springerlink:10.1007/978-3-642-32335-5_2}.

>>>>

\textbf{Dependencies}\\
At runtime, mahotas requires numpy to be present and installed. If compiling
from source, the Python headers and a \cpp{} compiler is required.

@@

Originally, this code was developed in the context of cellular image analysis.
However, the code was designed so that mahotas would contain functionality that
is not specific to cell image analysis and many computer vision pipelines can
make use of it.

This package (or earlier versions of it) have been used by
myself~\citep{Coelho2009,Coelho2010a} and close collaborators in several
publications~\citep{omerosearcher}. Other groups have used it in published
work, both in cell image analysis~\citep{CYTO:CYTO22034} and in other
areas~\citep{springerlink:10.1007/978-3-642-32335-5_2,ADFM:ADFM201300091}.
